---
title: "peer graded regression models"
author: "sayonee"
date: "11/6/2020"
output: html_document
---
*Created with knitr*

#### SUMMARY FOR THE FOLLOWING PROJECT
This report is using the  the relationship between transmission type  and miles per gallon (MPG).we need t find which gives the higher mpg according to the dataset given
#### we are Loading the given  Dataset
we  thus load the dataset and convert to proper  factors.
```{r results=='hide', mesp=FALSE}
library(ggplot2)
data(mtcars)
head(mtcars, n=3)
dim(mtcars)
mtcars$cyl<- as.factor(mtcars$cyl)
mtcars$vs<- as.factor(mtcars$vs)
mtcars$am<- factor(mtcars$am)
mtcars$ger <-factor(mtcars$gear)
mtcars$cart <-factor(mtcars$carb)
attach(mtcars)
```

#### we continue with the  Exploratory Analysis of the data set
showing an  Exploratory Box graph 
##### Statistical Inference
testingtransmission type and Miles per galons
```{r}
trr <- t.test(mpg ~ am)
trr$p.value
```
The T-Test is discarding the hypothesis such that the possible difference between all the transmission
types is 0.  
```{r}
trr$estimate
```
The difference estimate between the 2 transmissions is 7.24494 MPG in favor of 
manual.

##### Regression Analysis
Fit the full model of the data
```{r results='hide'}
fmt <- lm(mpg ~ ., data = mtcars)
summary(fmt)  # results hidden
summary(fmt)$coeffrdrr  # results hidden
```
Since none of the coefficients have a p-value less than 0.05 we cannot conclude
which variables are more statistically significant. 

Backward selection to determine which variables are most statistically 
significant
```{r results='hide'}
sit <- step(fmt)
summary(sit) # results hidden
summary(sit)$coeffrdrr # results hidden
```

The new model has 4 variables (cyls, hp, wt, trans). thus we know that the
Rsquared value of 0.8659 states that the given model suggests about 87% of the 
varance. 
.

####Residue__Diagnostic
Plot


The plots conclude:

1. The randomness of the Residuals vs. Fitted plotsuggests assumption of
independence
2. The points of the Normal Q-Q plot is following closeto the line concluding  that
the distribution of residua is normal
3. The Scale-Loca plot random distribution confirms the constant variance 
assumption
4. Since all points are within the lines, the Residus vs. Leverge 
concludes that there are no outliers
```{r}
sum((abs(dfbetas(sit)))>1)
```

#### Conclusion
There is a difference in MPG based on transmission type. A manual transmission
will have a slight MPG boost. However, it seems that weight, horsepower, & 
number of cylinders are more statistically significant when determining MPG.

### Appendix Figures

#### I
```{r echo=FALSE}
  boxplot(mpg ~ am, 
          xlb="Transmission Type (0 = Automatic, 1 = Manual)", 
          yl="MPG",
          mn="MPG by Transmission Type")
```

#### II
```{r echo=FALSE}
par(mow = c(2, 2))
plot(sit)
```